Ms 1

### 2017-07-21 ms1/ms1_display.Rmd
streamlining ms1

model_ci_cpkp = function(df) {
  model_ci(df) %>%
    mutate_at(vars(ci_range, ci_low, ci_high, estimate), function(x) x * 1000) %>%
    rename(cpkp=estimate)
}

@@

>>>>

model_ci_cpkp = function(df) {
  model_ci(df) %>%
    mutate_at(vars(ci_range, ci_low, ci_high, estimate), function(x) x*1000) %>%
    rename(cpkp=estimate)
}

@@

# Diagnoses

```{r}
read_tsv('tables/model_abx.tsv') %>%
  filter(term=='year') %>%
  mutate(model=case_when(.$model=='trimethoprim/sulfamethoxazole' ~ 'TMP/SMX',
                         .$model=='amoxicillin/clavulanate' ~ 'amox/clav',
                         TRUE ~ .$model)) %>%
  mutate(model=forcats::fct_reorder(model, estimate),
         cpkp=1000*estimate) %>%
  ggplot(aes(x=model, y=cpkp)) +
  geom_point() +
  geom_linerange(aes(x=model, ymin=0, ymax=cpkp)) +
  coord_flip() +
  xlab('') + ylab('Adjusted yearly change in claims per 1k bene. per yr') +
  scale_y_continuous(limits=c(-16, 17), breaks=c(-15, -10, -5, 0, 5, 10, 15)) +
  theme_minimal()
```
